Neural Power Unit \\-- A Bayesian Approach To Neural Arithmetic

### 2020-05-15 papers/main.tex
some plots

Neural Networks (NN) have proven to perform exceptionally well at function
approximation tasks\todo{cite universal approx}. The great approximation
performance unfortunately come at the cost of generalization beyond the
training domain\todo{cite something?}.  The inability to generalize to unseen
inputs is a fundamental problem that hints at a lack of \emph{understanding} of
the given task. The model merely memorizes the seen inputs and fails to
abstract the true learning task.

Neural Arithmetic Units aim to overcome this problem with units that are able
to represent simple arithmetic operations exactly. By composition of these
units it becomes possible to learn e.g. exponentials, sinus functions,
logarithms, etc. This promises to improve on the extrapolation capabilities of
NNs even on tasks that are beyond artificial arithmetic tasks such as learning
multiplication, or a certain power function \todo{cite some examples}.
\todo{mention ODEs as use case}

@@

\todo{put this in acknowledgements
all the results in this paper were create with the help of the following Julia
packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)}

\begin{table}
  \centering
  \caption{Comparison of different $2\times2$ layers on the task $(x,y)\rightarrow(xy,\frac{x}{y})$.
  $(x,y) \in \mathcal U^2(-2,2)$}
  \label{tab:label}
  \input{table_x*y_xdivy.tex}
\end{table}

>>>>

Neural Networks (NN) have proven to perform exceptionally well at function
approximation tasks\todo{cite universal approx}. This great approximation
performance unfortunately comes at the cost of generalization beyond the
training domain\todo{cite something?}.  The inability to generalize to unseen
inputs is a fundamental problem that hints at a lack of \emph{understanding} of
the given task. The model merely memorizes the seen inputs and fails to
abstract the true learning task.
This can be demonstrated by training a traditional, dense NN to approximate
three functions
\begin{align}
  \label{eq:approx_tasks}
  f(x) = e^x, && g(x) = \log(x), && h(x) = \sin(x)
\end{align}

\begin{figure}
  \centering
  \input{../plots/exp_log_sin/dense_exp.tex}
  \caption{}%
  \label{fig:}
\end{figure}

Neural Arithmetic Units aim to overcome this problem with units that are able
to represent simple arithmetic operations exactly. By composition of these
units it becomes possible to learn e.g. exponentials, logarithms, and power
functions. This promises to improve on the extrapolation capabilities of NNs
even on tasks that are beyond artificial arithmetic tasks such as learning
multiplication, or a certain power function \todo{cite some examples}.
\todo{mention ODEs as use case}

@@

\todo{put this in acknowledgements
all the results in this paper were create with the help of the following Julia
packages: \cite{rackauckas_differentialequationsjl_2017} + (Flux.jl)}
\todo{add sqrt and positive range to table~\ref{tab:compare_npu_npu_nalu}?}
\begin{table}
  \centering
  \caption{Comparison of different $2\times2$ layers on the task
  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
  \label{tab:compare_npu_npu_nalu}
  \input{table_x*y_xdivy.tex}
\end{table}
